Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-07-24 manuscript.tex
fix citation

\begin{figure}
\includegraphics{figure_2}
\caption{Exemplary analysis of the conformational dynamics of a pentapeptide backbone: (a) The Trp-Leu-Ala-Leu-Leu pentapeptide in licorice representation~\cite{humphrey1996vmd}.
(b) The VAMP-2 score indicates which of the tested featurizations contains the highest kinetic variance.
(c) The  sample density projected of the onto the first two time-lagged independent components (ICs) at lag time $\tau=0.5$ ns shows multiple density maxima and
(d) the time series of the first two ICs show rare transition events.
(e) The convergence behavior of the first four implied timescales indicates that a lag time of $\tau=0.5$ ns is suitable for MSM estimation.
(f) A Chapman-Kolmogorov test shows that an MSM estimated at lag time $\tau=0.5$ ns under the assumption of four metastable states accurately predicts the kinetic behavior on longer timescales.
In (e) and (f), the shaded areas indicate $95\%$ confidence intervals computed with a Bayesian sampling procedure.}
\label{fig:io-to-ck}
\end{figure}

>>>>

\begin{figure}
\includegraphics{figure_2}
\caption{Exemplary analysis of the conformational dynamics of a pentapeptide backbone: (a) The Trp-Leu-Ala-Leu-Leu pentapeptide in licorice representation~\cite{vmd}.
(b) The VAMP-2 score indicates which of the tested featurizations contains the highest kinetic variance.
(c) The  sample density projected of the onto the first two time-lagged independent components (ICs) at lag time $\tau=0.5$ ns shows multiple density maxima and
(d) the time series of the first two ICs show rare transition events.
(e) The convergence behavior of the first four implied timescales indicates that a lag time of $\tau=0.5$ ns is suitable for MSM estimation.
(f) A Chapman-Kolmogorov test shows that an MSM estimated at lag time $\tau=0.5$ ns under the assumption of four metastable states accurately predicts the kinetic behavior on longer timescales.
In (e) and (f), the shaded areas indicate $95\%$ confidence intervals computed with a Bayesian sampling procedure.}
\label{fig:io-to-ck}
\end{figure}
